Turbulence in compact to giant HII regions

### 2022-01-21 strucfunc_paper.tex
Javier changes 2022-01-21

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

\textit{Note: First I was using the luminosities values from the table of the Git page for the regression analysis. But I change them according to the bibliography when writing section 2. The values are quite consistent but for Carina there was some difference. From \SI{e39}{erg.s^{-1}} to \SI{e38}{erg.s^{-1}}.}
The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

>>>>

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 2.7    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.25 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(9 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 1.4) \log \sigma -(36 \pm 1)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)
